### 2012-05-24 docs/visualization/visualization.tex
point to AmrPostprocessing
fix compilation
quick addition of notes for visit on Lens.  Need to be LaTeX-ified

%-----------------------------------------------------------------------------
% data_procesing
%-----------------------------------------------------------------------------
\section{Visualizing with {\tt data\_processing} scripts}
\label{sec:vis:python}

{\tt data\_processing/python\_plotfile} provide a simple commandline
tool for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

>>>>

\subsection{Remote Visualization on Lens}

in .bashrc, add:

export PATH=''/sw/analysis-x64/visit/bin/'':\$PATH

in visit on bender:

setup a new host

   options -> host profiles

      'new'

   under 'host settings' tab:

      host nickname: lens
      remote host name: lens.ccs.ornl.gov

      make sure your username is correct

      check 'tunnel data connections through SSH'

   under 'launch profiles' tab:

       'new'
       call it parallel

       under 'parallel' tab:

         check 'lauch parallel engine'
         parallel launch method: qsub/mpirun
         partition: computation
         default number of processors: 8
         default number of nodes: 2
         default bank/account: AST006
         default time limit: 00:30:00

save the host setting by Options -> save settings

then 'open', from the drop down list at the top, select lens.  You
will be prompted for your password.  After that, you can navigate to
the directory on lens with the data.

%-----------------------------------------------------------------------------
% data_procesing
%-----------------------------------------------------------------------------
\section{Python visualization scripts}
\label{sec:vis:python}

{\tt AmrPostprocessing/F\_Src/python\_plotfile} provide a simple commandline
tool for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.
